{Gravitational wave sources in our Galactic backyard:}\\{Predictions for BHBH, BHNS and NSNS binaries detectable with LISA

### 2021-11-26 paper/tex/paper.tex
update keywords
rename bib file for arxiv
Updates from Overleaf

\title{{\large Gravitational wave sources in our Galactic backyard:}\\{\normalsize Models for detecting BHBH, BHNS and NSNS binaries with LISA}}

@@

\author[0000-0002-6411-8695]{N. Frankel}
\affiliation{Max Planck Institute for Astronomy, Königstuhl 17, D-69117 Heidelberg, Germany}

@@

\keywords{gravitational waves, LISA, black hole, neutron star, binary stars}

>>>>

\title{{Gravitational wave sources in our Galactic backyard:}\\{Predictions for BHBH, BHNS and NSNS binaries detectable with LISA}}

@@

\author[0000-0002-6411-8695]{N. Frankel}
\affiliation{Canadian Institute for Theoretical Astrophysics, University of Toronto, 60 St. George Street, Toronto, ON M5S 3H8, Canada}
\affiliation{Max Planck Institute for Astronomy, K\"onigstuhl 17, D-69117 Heidelberg, Germany}
\affiliation{David A. Dunlap Department for Astronomy and Astrophysics, University
of Toronto, 50 St. George Street, Toronto, ON M5S 3H4, Canada}

@@

\keywords{gravitational waves, gravitational wave detectors, compact objects, stellar mass black holes, neutron stars, binary stars, stellar evolution, pulsars}

### 2021-11-26 paper/tex/sections/discussion.tex
Updates from Overleaf

We highlight the possible role of dynamical formation in globular clusters, which was investigated by \citet{Kremer+2018}. For a nominal 4-year LISA mission, they estimate 21 sources in total will have SNR $> 7$, of which 7 are BHBHs, 0 are BHNSs and 1 is a NSNS \citep[see Table~1][]{Kremer+2018}. In this case, we predict that the sources formed through isolated binary formation will be dominant in nearly every model variation.

In addition, \citet{Banerjee+2020} investigates formation of LISA detectable BHBHs in young massive and open stellar clusters. and estimates approximately 128 BHBHs with SNR $>5$ in a 5-year LISA mission \citep[see Table~1, Column 9][]{Banerjee+2020}. Note that this total uses a slightly longer mission length and a lower SNR threshold than those used in this paper. Nevertheless, this rate is on the same order as our predictions for LISA BHBHs.

>>>>

We highlight the possible role of dynamical formation in globular clusters. \citet{Kremer+2018} predict, for a nominal 4-year LISA mission, that 21 sources will have SNR $> 7$, of which 7 are BHBHs, 0 are BHNSs and 1 is a NSNS \citep[see Table~1][]{Kremer+2018}. This is significantly lower than the rates we predict for nearly every model variation. If true, this would mean that formation through isolated binary formation will dominate the LISA detections.

\citet{Banerjee+2020} investigates formation of LISA detectable BHBHs in young massive and open stellar clusters and estimates approximately 128 BHBHs with SNR $>5$ in a 5-year LISA mission \citep[see Table~1, Column 9][]{Banerjee+2020}. Although this is similar to the number we predict for our fiducial model, we note these authors adopt a threshold SNR required for a detection that is lower and a mission length is slightly longer than what is typically assumed (i.e. SNR $>7$ and 4 years, as we have also adopted in our work). We expect that, after correcting for this and making a fair comparison, our fiducial model predicts about twice as many detections.

The contribution of triples systems \citep[e.g.][]{Antonini+2017}, or even higher order multiple systems \citep[e.g.][]{Vynatheya+2021} will likely also be of interest, in particular for the formation of eccentric sources. We are, however, not aware of specific predictions for the detection rates that we can compare to directly.

### 2021-11-26 paper/tex/sections/variations.tex
Updates from Overleaf

In model \modCaseBB{} we enforce that case BB mass transfer is always unstable, such that it always leads to a CE. Note that this is slightly different from model E from \citet{Broekgaarden+2021}, as we allow Helium Hertzsprung Gap donors to survive a common-envelope (but still apply the pessimistic CE assumption in all other cases). We make this change since, otherwise, the model would effectively exclude any systems that evolve through case BB mass transfer and kill nearly all NSNS systems. As expected, in model \modCaseBB{}, we find that case BB systems form through a common-envelope phase rather than only stable mass transfer (see Fig.~\ref{fig:formation_channels}). This model gives the lowest NSNS rate of all of our variations, which is a factor of 3 lower than our fiducial rate. We also find a reduction of the BHNS systems by a factor 2. The BHBH systems are not significantly affected, as expected, since case BB mass transfer does not play a role for high mass progenitors.

>>>>

In model \modCaseBB{} we enforce that case BB mass transfer is always unstable, such that it always leads to a CE. Note that this is slightly different from model E described in  \citet{Broekgaarden+2021}. In their work the pessimistic approach to CE evolution is implemented such that all HG stars are excluded including helium stars in the helium shell burning phase. This, in combination with the assumption that case BB mass transfer is always unstable, effectively leads to the exclusion of all systems that originate through this channel. We are interested in NSNS systems, which are frequently formed through this channel in our simulations. Therefore, we adapted this model to only exclude H-rich HG donors, but allow systems with donors that are helium stars in the helium shell burning phase to survive a CE phase.

As expected, in model \modCaseBB{}, we find that case BB systems form through a common-envelope phase rather than only stable mass transfer (see Fig.~\ref{fig:formation_channels}). This model gives the lowest NSNS rate of all of our variations, which is a factor of 3 lower than our fiducial rate. We also find a reduction of the BHNS systems by a factor 2. The BHBH systems are not significantly affected, as expected, since case BB mass transfer does not play a role for high mass progenitors.
